### 2023-01-18 paper.tex
Feedback for Section V

	The task of generating this repository was completed through the following sub-tasks::
	\begin{itemize}
		\item \textit{Selecting a data source}: Pierro et al. list some sources that can be used to collect smart contract source code from the Web \cite{pierro}. These resources include commonly known code repository hosting platforms (GitHub\footnote{https://github.com}, GitLab\footnote{https://about.gitlab.com} and BitBucket\footnote{https://bitbucket.org}). Additionally, several Ethereum block explorers are available. These services allow for different kinds of interactions with and the analysis of the Ethereum blockchain. EtherScan\footnote{https://etherscan.io/} and EtherChain\footnote{https://etherchain.org/} are two examples of block explorers. In their paper, Pierro et al. use the API of EtherScan to collect verified smart contracts and store them in a database~\cite{pierro}. However, block explorers can only provide the version of the smart contract that is deployed on the blockchain, but not its previous versions. Hence, for the work at hand, GitHub was selected as the source of the data in the repository. GitHub also provides a large volume of source files available and integration with Git, which ensures availability of versions of the source files. Other similar repositories such as GitLab or BitBucket have severely limited or pay-walled provisions for searching and crawling. GitHub, on the other hand, ensures accessibility of the code and its versions through its APIs. GitHub's APIs also allow the user to search for and download files based on the licensing scheme adopted by the developers. This enables the script introduced in this paper to allow users to distinguish between files with viral and non-viral licenses. 
		\item \textit{Automating the data collection process}: To perform data collection from GitHub automatically, a python script was implemented. The script is based on the \textit{github-searcher}\footnote{https://github.com/ipa-lab/github-searcher} written by Schröder et al. to run a stratified search for code snippets on all public repositories~\cite{schroder}. This is done to circumvent the limitation of 5000 requests per hour per API-token imposed by the GitHub API in its free version.
		\item \textit{Collecting the required files}: The implemented script prepares the search by requesting the user for the following information:
		\begin{itemize}
			\item \texttt{database}: the name of an existing database to store the results in. If not provided, the script creates a database file called \texttt{results.db}.
			\item \texttt{statictics}: the name of an existing file to store the search statistics in.
			\item \texttt{min-size}: the minimum file size to search for and collect.
			\item \texttt{max-size}: the maximum file size to search for and collect. GitHub itself imposes a limit of 384 KB on the file size.
			\item \texttt{stratum-size}: the lengths of file-size ranges to be used for the stratified search.
			\item \texttt{no-throttle}: to disable request throttling.
			\item \texttt{search-forks}: this option, if set to \texttt{true}, adds \texttt{fork:true} to the GitHub search query and includes forks of repositories in the search. This expands the field of search but risks including duplicate files in the results.
			\item \texttt{license-filter}: if set to \texttt{true}, filters the search results to include only open-source licensed repositories.
			\item \texttt{github-token}: lets the user enter a GitHub API token in order to access the search APIs. If an API token is present in the environment variables, it is used automatically.
		\end{itemize}

@@

		During experimentation, this resulted in a collection of 163,961 Solidity files, including 299,437 commits. At this point, the script has collected all data it needs to store in the persistent storage to create the repository. All these solidity files have their complete version history and metadata that are the distinctive features of this repository.

>>>>

	The task of generating this repository was completed through the following sub-tasks::
	\begin{itemize}
		\item \textit{Selecting a data source}: Pierro et al. list some sources that can be used to collect smart contract source code from the Web \cite{pierro}. These resources include commonly known code repository hosting platforms (GitHub\footnote{https://github.com}, GitLab\footnote{https://about.gitlab.com} and BitBucket\footnote{https://bitbucket.org}). Additionally, several Ethereum block explorers are available. These services allow for different kinds of interactions with and the analysis of the Ethereum blockchain. Etherscan\footnote{https://etherscan.io/}\todo{Only provide each URL only once} and EtherChain\footnote{https://etherchain.org/} are two examples of block explorers\todo{This is not the third time Etherscan is mentioned. As written above, introduce it at one point. Then, you can refer to that here.}. In their paper, Pierro et al. use the API of Etherscan to collect verified smart contracts and store them in a database~\cite{pierro}\todo{This is something which rather fits into the RW discussion, not here.}. However, block explorers can only provide the version of the smart contract that is deployed on the blockchain, but not its previous versions\todo{I think this has now been mentioned several times, hasn't it? If you think it's a good idea to repeat things (e.g., since the reader may have forgotten about them), it's best to write something like ``As described in Section X.Y'', or ``As written above''.}. Hence, for the work at hand, GitHub was selected as the source of the data in the repository. GitHub also provides a large volume of source files available and integration with Git, which ensures availability of versions of the source files. Other similar repositories such as GitLab or BitBucket have severely limited or pay-walled provisions for searching and crawling. GitHub, on the other hand, ensures accessibility of the code and its versions through its APIs. GitHub's APIs also allow the user to search for and download files based on the licensing scheme adopted by the developers. This enables the script introduced in this paper to allow users to distinguish between files with viral and non-viral licenses\todo{Again: That this might be an issue has been mentioned very briefly as a side-note. But that this is a central aspect in the design (sine the script becomes necessarY) is still unknown to the reader}. 
		\item \textit{Automating the data collection process}: To perform data collection from GitHub automatically\todo{Again: It is still not known to the reader why the data collection needs to be done by him-/herself.}, a Python script was implemented. The script is based on the \textit{github-searcher}\footnote{https://github.com/ipa-lab/github-searcher} written by Schröder et al. to run a stratified search for code snippets on all public GitHub repositories~\cite{schroder}. This is done to circumvent the limitation of 5000 requests per hour per API-token imposed by the GitHub API in its free version.
		\item \textit{Collecting the required files}: The implemented script prepares the search for particular smart contracts by requesting the user for the following information:
		\begin{itemize}
			\item \texttt{database}: the name of an existing database to store the results in. If not provided, the script creates a database file called \texttt{results.db}.
			\item \texttt{statictics}: the name of an existing file to store the search statistics in.
			\item \texttt{min-size}: the minimum file size to search for and collect.
			\item \texttt{max-size}: the maximum file size to search for and collect. GitHub itself imposes a limit of 384 KB on the file size.
			\item \texttt{stratum-size}: the lengths of file-size ranges to be used for the stratified search.
			\item \texttt{no-throttle}: to disable request throttling.
			\item \texttt{search-forks}: this option, if set to \texttt{true}, adds \texttt{fork:true} to the GitHub search query and includes forks of repositories in the search. This expands the field of search but risks including duplicate files in the results.
			\item \texttt{license-filter}: if set to \texttt{true}, filters the search results to include only open-source licensed repositories.
			\item \texttt{github-token}: lets the user enter a GitHub API token in order to access the search APIs. If an API token is present in the environment variables, it is used automatically.

@@

		During experimentation, this resulted in a collection of 163,961 Solidity files, including 299,437 commits. At this point, the script has collected all data it needs to store in the persistent storage to create the repository. All these 
		Solidity files have their complete version history and metadata that are the distinctive features of this repository.
